Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
chore: more on the environment

\subsection{Simulated environment}
The proposed multi-agent environment, which we design to evaluate the efficacy of the neighboring-based strategies,
 consists of a two-dimensional Euclidean space 
 populated by a variable number of \emph{targets} and \emph{agents}, 
 whose initial positions are randomly distributed across the space.
%
The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
%
The observation space of each agent consist of a tuple of three elements: %% TODO CHECK AGAIN
\begin{enumerate*}[label=(\roman*)]
  \item number of the closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of the closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
The action space for each agent is discrete, 
consisting of eight possible movements corresponding 
to the cardinal and diagonal directions on a grid

@@

\subsection{Evaluation metrics} 
In our experiments, we employed two metrics to evaluate the performance of the learning
  agents and monitor the quality of the training process, namely: 
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Mean Episode Reward}; and
    \item \emph{Mean Episode Length}.
  \end{enumerate*}

\paragraph{Mean Episode Reward} 
The Mean Episode Reward measures the average cumulative reward the agent obtains during each episode, 
  serving as a direct indicator of how well each agent is performing in achieving its task.
%
Formally, for $N$ episodes, the mean reward $R_{mean}$ is computed as:
  \[ R_{mean} = \frac{1}{N} \sum_{i=1}^{N} R_i \]
  where $R_i$ is the total reward obtained in the $i$-th episode.

\paragraph{Mean Episode Length}
On the other hand, the Mean Episode Length represents the average number of time steps (or actions) 
  the agent takes per episode before reaching the terminal state. 
%
It provides insights into the agent's efficiency in completing tasks, especially in environments 
  where shorter episodes indicate better performance.
%
The mean episode length $L_{mean}$ is calculated as:
  \[ L_{mean} = \frac{1}{N} \sum_{i=1}^{N} L_i \]
  where $L_i$ is length of $i$-th episode.

>>>>

\subsection{Simulated environment}
The proposed multi-agent environment, which we design to evaluate the efficacy of the neighboring-based strategies,
 consists of a two-dimensional Euclidean space 
 populated by a variable number of \emph{targets} and \emph{agents}, 
 whose initial positions are randomly distributed across the space.
%
The environment is considered solved when all targets are collected, terminating the episode. 
To prevent infinitely long episodes, a maximum time limit of T = 300 steps is imposed. 
If all items are collected before this limit, the episode terminates early.
The agents' objective  is to collaboratively collect all the targets in the environment, minimizing the total retrivial time.
%
The observation space of each agent consist of a tuple of three elements: %% TODO CHECK AGAIN
\begin{enumerate*}[label=(\roman*)]
  \item number of the closest agents that the agent is able to see (thus, forming a neighborhood);
  \item number of the closest items that the agent is able to see;
  \item memory of past states, thus encoding also temporal information, helping each agent to understand 
    the evolution of the environment.
\end{enumerate*} 
%
The action space for each agent is discrete, 
consisting of eight possible movements corresponding 
to the cardinal and diagonal directions on a grid.
%

@@

\subsection{Evaluation metrics} 
In our experiments, we employed two metrics to evaluate the performance of the learning
  agents and monitor the quality of the training process, namely: 
  \begin{enumerate*}[label=(\roman*)]
    \item \emph{Mean Episode Reward} ($R_{mean}$); and
    \item \emph{Mean Episode Length} ($L_{mean}$).
  \end{enumerate*} 
%
$R_{mean}$ measures the average cumulative reward the agent obtains during each episode, 
  serving as a direct indicator of how well each agent is performing in achieving its task.
%
Formally, for $N$ episodes, the mean reward $R_{mean}$ is computed as:
  \[ R_{mean} = \frac{1}{N} \sum_{i=1}^{N} R_i \]
  where $R_i$ is the total reward obtained by all agents in the $i$-th episode. 
  Formally, for a certain episode $i$, composed of $n$ agents, last $T$ time steps, the total reward $R_i$ is calculated as:
  \[ R_i = \sum_{t=0}^{T} \sum_{j=1}^{n} r^j_t \]
  where $r^j_t$ is the reward obtained by agent $j$ at time step $t$.

On the other hand, the $L_{mean}$ represents the average number of time steps needed to reaching the terminal state, i.e., no more items to collect. 
%
It provides insights into the agent's efficiency in completing tasks, especially in environments 
  where shorter episodes indicate better performance.
%
The mean episode length $L_{mean}$ is calculated as:
  \[ L_{mean} = \frac{1}{N} \sum_{i=1}^{N} L_i \]
  where $L_i$ is length of $i$-th episode.
